Tracing the Stellar Halo of Massive Galaxies to 100 kpc at $0.3<z<0.5$ using the Hyper Suprime-Cam

### 2017-05-30 draft/paper1_jenny.tex
Edit 1-D profile

    The right panel of Fig~\ref{fig:avg_prof} compares our results with several 
    previous works. 
    So far, deep \mden{} profiles of massive galaxies are rarely available. 
    Even in the nearby universe, it is still not easy to reach to the very outskirt
    of massive galaxy due to several technical issues (e.g. 
    \citealt{Capaccioli2015, Iodice2016, Iodice2017, Spavone2017, Mihos2017})

    Although it is relative easier to reach to the very outskirt of massive galaxy 
    in the nearby universe, the small volume limits the number of available 
    galaxies at high-mass end. 
    Most previous studies often focus more on the surface brightness profiles, 
    and they also depend on stacking techniques or model-dependent method to 
    study the structure of massive galaxies in their outskirts.

    Most previous studies have relied on stacking techniques to measure surface 
    brightness profiles out to large radii.
    So far, the surface brightness profiles of massive galaxies out to such large 
    radii was mostly derived via image stacking technique that suffers from several 
    systematic issues (e.g. \citealt{Tal2011, DSouza2015}; but also see:
    \citealt{Capaccioli2015}); and the \mden{} profiles are even more rarely 
    available.

    \citet{Huang2013a} derived \mden{} profiles for a small sample of very nearby 
    ellipticals (within 100 Mpc; median \logms{} ${\sim} 11.3$ based on shallower 
    images) from the Carnegie-Irvine Galaxy Survey (CGS, \citealt{CGS1}). 
    Because this is a very low redshift sample, these profiles are accurate to 
    smaller scales, $r=1$ kpc. 
    The \citet{Huang2013a} profiles show good agreement with ours in the region of 
    overlap and out to 50 kpc. 
    CGS images are deeper than SDSS images in the $r$-band, but the median 
    profile from \citet{Huang2013a} still only reaches ${\sim} 50$ kpc for $z{\sim} 0$ 
    massive galaxies.
    Meanwhile, our deep HSC images can reliably deliver individual \mden{} profiles 
    for $z{\sim} 0.4$ galaxies out to at least 100 kpc.

@@

    Finally, we also compare with the predicted median \mden{} profile of central 
    galaxies in massive halos ($13.5 < \log M_{200,c} < 14.0$) from cosmological 
    simulation where the \mden{} profiles of galaxies are calculated using the 
    particle-tagging technique (e.g. \citealt{Cooper2010}).

    The simulated \mden{} profile is also affected by limited resolution in the 
    center, but it is already quite similar to the median \mden{} profile for 
    the $11.6 <$ \logmtot{} $< 11.8$ bin within 40 kpc. 
    However, compared with our data, this simulation predicts stellar envelope that
    are too prominent at this halo mass. 
    This types of comparisons between our HSC data and predictions from simulations 
    will help to fine-tune simulations and to also investigate the main physical 
    mechanisms that drive the assembly of massive galaxies and the build up of 
    stellar envelopes.

>>>>

    The right panel of Fig~\ref{fig:avg_prof} compares our results with several 
    previous works. 
    So far, deep \mden{} profiles of massive galaxies are rarely available. 
    Even in the nearby universe, it is still not easy to reach to the very outskirt
    of massive galaxy due to technical difficulties (e.g. 
    \citealt{Capaccioli2015, Iodice2016, Iodice2017, Spavone2017, Mihos2017})
    The small volume of local universe also limits the number of available 
    galaxies at high-mass end.
    Most previous studies often focus more on the surface brightness profiles, 
    and they also depend on stacking techniques or model-dependent method to 
    study the structure of massive galaxies in their outskirts (e.g. 
    \citealt{Tal2011, DSouza2015}), both of which suffer from several systematic 
    issues.

    \citet{Huang2013a} derived \mden{} profiles for a small sample of very nearby 
    ellipticals (within 100 Mpc; median \logms{} ${\sim} 11.3$ based on shallower 
    images) from the Carnegie-Irvine Galaxy Survey (CGS, \citealt{CGS1}). 
    Because this is a very low redshift sample, these profiles are accurate to 
    smaller scales, $r=1$ kpc. 
    The \citet{Huang2013a} \mden{} profiles show good agreement with ours in the 
    region of overlap and out to 50 kpc although their \m2l{} are derived in 
    slightly different ways.
    CGS images are deeper than SDSS images in the $r$-band, but the median 
    profile from \citet{Huang2013a} still only reaches ${\sim} 50$ kpc for $z{\sim} 0$ 
    massive galaxies.
    Meanwhile, our deep HSC images can reliably deliver individual \mden{} profiles 
    for $z{\sim} 0.4$ galaxies out to at least 100 kpc.

@@

    Finally, we also compare with the predicted median \mden{} profile of central 
    galaxies in massive halos ($13.5 < \log M_{200,c} < 14.0$) from cosmological 
    simulation where the \mden{} profiles of galaxies are calculated using the 
    particle-tagging technique (e.g. \citealt{Cooper2010}). 
    The simulated \mden{} profile is also affected by limited resolution in the 
    center, but it is already quite similar to the median \mden{} profile for 
    the $11.6 <$ \logmtot{} $< 11.8$ bin within 40 kpc. 
    However, outside 40 kpc, the particle tagging method seems to predict a too 
    prominent stellar halo that has much shallower slope compared to our data.

    Although the particle tagging method is not considered the best way to simulate
    the stellar mass distributions of massive galaxies, this comparison can already 
    demonstrate the advantages of our \mden{} profiles. 
    Such comparisons between our HSC data and predictions from more advanced 
    hydrodynamic simulations will help fine-tune simulations and also investigate 
    the physical mechanisms that drive the assembly of massive galaxies and the 
    build up of stellar halos.
